Results (Julia)

### 2025-01-07 notebooks/01_results_julia.qmd
feat: update effect of time lag T

```{julia}
df = load_taus(; unique_f=missing)
jno_df = load();
wind_df = load(; name="Wind", ts=missing);
```

@@

let tdf = Discontinuity.remove_duplicates(df)
    plot_nrow(tdf, :r, 0.5, :tau; normalize = normalize_by_all, xlabel=r_lab, clabel="T")
    easy_save("ocr/juno_tau_r")
end
```

>>>>

```{julia}
df = load_taus(; unique_f=missing)
jno_df = load();
wind_df = load(; name="Wind", ts=nothing);
```

@@

let tdf = Discontinuity.remove_duplicates(df)
    plot_nrow(tdf, :r, 0.5, :tau; normalize = normalize_by_all, xlabel=r_lab, clabel="T")
    ylims!(0, 0.7)
    easy_save("ocr/juno_T_r")
end
```
